Do Automated Fault Localization Techniques Work For REST APIs?

### 2024-06-05 CS563-Project/Paper/paper.tex
Commit before making major changes - to write about findings

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{tcolorbox}
\usepackage{array}
% \usepackage{lscape}
\usepackage{pdflscape}
\usepackage{rotating}

\usetikzlibrary{shapes.geometric, arrows}

@@

\author{\IEEEauthorblockN{Aakash Kulkarni}
\IEEEauthorblockA{\textit{School of EECS} \\ % --- To do ---
\textit{Oregon State University}\\ % --- To do ---
Corvallis, United States \\ % --- To do ---
kulkaraa@oregonstate.edu}
\and
\IEEEauthorblockN{Soon Song Cheok}
\IEEEauthorblockA{\textit{School of EECS} \\ % --- To do ---
\textit{Oregon State University}\\ % --- To do ---
Corvallis, United States \\ % --- To do ---
cheoks@oregonstate.edu}
\and
\IEEEauthorblockN{Shreyes Joshi}
\IEEEauthorblockA{\textit{School of EECS} \\ % --- To do ---
\textit{Oregon State University}\\ % --- To do ---
Corvallis, United States \\ % --- To do ---
joshish@oregonstate.edu}
}

@@

% \subsection{Problem statement}
    REST APIs (Representational State Transfer) have become backbone of the modern web and cloud applications. They facilitate seamless interactions between client and server through stateless communication, enabling services to be scalable, reliable, and easily integrateable ~\cite{li2016} ~\cite{neumann2018}. Basically, REST APIs are a set of rules and standards  defined by OpenAPI ~\cite{ed-douibi2018} used to enable communication between different software applications over the internet. They are built around the use of standard HTTP methods such as GET, POST, PUT, and DELETE to interact with resources, which are any kind of data or service that can be named on a network.
    Given their critical role, the effective identification and resolution of faults within REST APIs remain a significant challenge ~\cite{barbir2007}, prompting the need for research on how fault localization techniques work to their unique structure and functionality.

    % \todo{What is the problem statement that you plan to solve?}

% \subsection{Motivation}
    As systems that rely on REST APIs grow in scale and complexity  ~\cite{khare2004} , minor faults can escalate into major disruptions, impacting user experience and business operations. 
    This research is motivated by the need to evaluate how well current fault localization techniques perform in the unique context of REST APIs. 
    The goal is to determine if these techniques can indeed be applied effectively to REST APIs and, if so, to explore which types of faults are more amenable to being localized. 
    This understanding could potentially allow developers to more efficiently diagnose and address issues, thereby enhancing the stability and performance of REST API-based systems.

    % \todo{Why should anyone care about solving that problem?}

% \subsection{Relation with software engineering research}

@@

    % \todo{How is the problem related to software engineering research? What is already known about that problem space, and what is still unknown that you are interested in solving?}

% \subsection{Key Insight or Idea}
    The primary objective of this research is to evaluate the effectiveness of existing fault localization techniques within the unique context of REST APIs, which feature a mix of code and non-code artifacts. 
    This study will systematically apply established fault localization methods like BLUES ~\cite{ManishBluesFaultLocalization} and LLMAO ~\cite{LLMAOFaultLocalization} to a dataset of REST API faults. 
    This dataset will be meticulously developed to represent a wide range of faults typical in REST APIs and classified according to an existing comprehensive taxonomy derived from previous research.

    This approach will enable us to assess the applicability of these fault localization techniques to REST APIs by determining how effectively they can identify and localize different types of faults. 
    % Importantly, this research does not assume the prior effectiveness of these techniques in REST API contexts but seeks to establish empirical evidence of their performance. 
    The analysis will provide insights into whether traditional fault localization methods are suited to the complexities of REST APIs, especially considering their unique structural and functional characteristics.

    % \todo{What is the high-level approach that you would like to explore to solve the problem? Why you feel you can succeed with that approach in 5 weeks?}

% \subsection{Assumptions}
    Our assumptions:
    \begin{itemize}
        % \item \textit{Assumption 1:} It is assumed that the faults in the dataset are correctly classified according to the existing comprehensive taxonomy ~\cite{automatedTestTaxonomy} .
        \item \textit{Assumption:} Assume that the selected fault localization techniques are suitable for application to REST APIs, despite their original design for conventional software systems. This includes the assumption that these techniques can handle the unique challenges posed by REST APIs, such as dealing with non-code artifacts.
    \end{itemize}

    % \todo{What kind of assumptions will you need to make for your choice of solution?}

% \subsection{Research questions}
    The primary research questions are formulated as follows:
    \begin{itemize}
        \item \textbf{RQ1:} What categories of faults are most effectively localized by current techniques?
        \item \textbf{RQ2:} Which fault localization technique is highly effective in the context of REST APIs?
    \end{itemize}
    % \todo{What research question(s) will you answer?}

% \subsection{Evaluation Dataset}
For the evaluation dataset, we will manually select the issues from the GitHub services and their fixes from REST API projects that utilize Spring Boot or Jersey frameworks. These GitHub services are used in the paper  \textit{Generating REST API Specifications through Static Analysis} by Manish et al ~\cite{ManishRestServices}
This dataset will encompass various categories of faults identified in REST APIs. By analyzing repositories and commit histories, we will extract specific instances where bugs have been documented and subsequently fixed. 
The categorization of these faults will be categorized with an established taxonomy of API faults ~\cite{automatedTestTaxonomy} , ensuring that each bug is classified according to its nature and impact. This rigorous dataset compilation aims to provide a comprehensive basis for testing fault localization techniques within a controlled, relevant environment.

% \subsection{Evaluation metrics}
For evaluation of fault localization techniques using the dataset derived from REST APIs employing Spring Boot and Jersey frameworks will be measured by Top-k accuracy, and EXAM score.
These metrics will collectively provide a thorough assessment of each fault localization technique's ability to detect and accurately categorize faults in REST APIs, contributing to a detailed understanding of their practical utility and areas for improvement.

    % \todo{How will you know that you have solved the problem successfully? In other words, how will you evaluate your solution?}

@@

% The fault taxonomy had 4 Major fault types where each major fault type has sub-categories from ~\cite{automatedTestTaxonomy}, in total we had 19 categories of faults we can divide into.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{tcolorbox}
\usepackage{array}

@@

\author{\IEEEauthorblockN{Aakash Kulkarni}
\IEEEauthorblockA{\textit{School of EECS} \\
\textit{Oregon State University}\\
Corvallis, United States \\
kulkaraa@oregonstate.edu}
\and
\IEEEauthorblockN{Soon Song Cheok}
\IEEEauthorblockA{\textit{School of EECS} \\
\textit{Oregon State University}\\
Corvallis, United States \\
cheoks@oregonstate.edu}
\and
\IEEEauthorblockN{Shreyes Joshi}
\IEEEauthorblockA{\textit{School of EECS} \\
\textit{Oregon State University}\\
Corvallis, United States \\
joshish@oregonstate.edu}
}

@@

    REST APIs (Representational State Transfer) have become backbone of the modern web and cloud applications. 
    They facilitate seamless interactions between client and server through stateless communication, enabling services to be scalable, reliable, and easily integrateable ~\cite{li2016} ~\cite{neumann2018}. 
    Basically, REST APIs are a set of rules and standards  defined by OpenAPI ~\cite{ed-douibi2018} used to enable communication between different software applications over the internet. They are built around the use of standard HTTP methods such as GET, POST, PUT, and DELETE to interact with resources, which are any kind of data or service that can be named on a network.
    Given their critical role, the effective identification and resolution of faults within REST APIs remain a significant challenge ~\cite{barbir2007}, prompting the need for research on how fault localization techniques work to their unique structure and functionality.

    As systems that rely on REST APIs grow in scale and complexity  ~\cite{khare2004} , minor faults can escalate into major disruptions, impacting user experience and business operations. 
    This research is motivated by the need to evaluate how well current fault localization techniques perform in the unique context of REST APIs. 
    The goal is to determine if these techniques can indeed be applied effectively to REST APIs and, if so, to explore which types of faults are more amenable to being localized. 
    This understanding could potentially allow developers to more efficiently diagnose and address issues, thereby enhancing the stability and performance of REST API-based systems.

@@

    The primary objective of this research is to evaluate the effectiveness of existing fault localization techniques within the unique context of REST APIs, which feature a mix of code and non-code artifacts. 
    This study will systematically apply established fault localization methods like BLUES ~\cite{ManishBluesFaultLocalization} and LLMAO ~\cite{LLMAOFaultLocalization} to a dataset of REST API faults. 
    This dataset will be meticulously developed to represent a wide range of faults typical in REST APIs and classified according to an existing comprehensive taxonomy derived from previous research.

    This approach will enable us to assess the applicability of these fault localization techniques to REST APIs by determining how effectively they can identify and localize different types of faults. 
    The analysis will provide insights into whether traditional fault localization methods are suited to the complexities of REST APIs, especially considering their unique structural and functional characteristics.

    Our assumptions:
    \begin{itemize}

        \item \textit{Assumption:} Assume that the selected fault localization techniques are suitable for application to REST APIs, despite their original design for conventional software systems. This includes the assumption that these techniques can handle the unique challenges posed by REST APIs, such as dealing with non-code artifacts.
    \end{itemize}

    The primary research questions are formulated as follows:
    \begin{itemize}
        \item \textbf{RQ1:} What categories of faults are most effectively localized by current techniques?
        \item \textbf{RQ2:} Which fault localization technique is highly effective in the context of REST APIs?
    \end{itemize}

For the evaluation dataset, we will manually select the issues from the GitHub services and their fixes from REST API projects that utilize Spring Boot or Jersey frameworks. These GitHub services are used in the paper  \textit{Generating REST API Specifications through Static Analysis} by Manish et al ~\cite{ManishRestServices}
This dataset will encompass various categories of faults identified in REST APIs. By analyzing repositories and commit histories, we will extract specific instances where bugs have been documented and subsequently fixed. 
The categorization of these faults will be categorized with an established taxonomy of API faults ~\cite{automatedTestTaxonomy} , ensuring that each bug is classified according to its nature and impact. This rigorous dataset compilation aims to provide a comprehensive basis for testing fault localization techniques within a controlled, relevant environment.

For evaluation of fault localization techniques using the dataset derived from REST APIs employing Spring Boot and Jersey frameworks will be measured by Top-k accuracy, and EXAM score.
These metrics will collectively provide a thorough assessment of each fault localization technique's ability to detect and accurately categorize faults in REST APIs, contributing to a detailed understanding of their practical utility and areas for improvement.

@@
